---
title: "model"
author: "sameera talafha"
date: "11/10/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
set.seed(1989)
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(corrplot)
library(caret)
library(GGally)
library(tree)
library(randomForest)
library(PerformanceAnalytics)
library(psych)
ins=read.csv("insurance.csv")
ins$age2 <- ins$age^2
ins$bmi30 <- ifelse(ins$bmi >= 30, 1, 0)
s_dev=sd(ins$charges)
mean_val=mean(ins$charges)
s_dev_bmi=sd(ins$bmi)
mean_bmi=mean(ins$bmi)
ins$bmi = scale(ins$bmi)
ins$charges=(ins$charges*s_dev)+mean_val
ins$smoker_num=ifelse(ins$smoker=="yes",1,0)
ins$child_cat = as.factor(ins$children)
head(ins)

```


### Transform the Response

The powerTransform() function in the car package determines the optimal power at which you should raise the outcome variable (in this case, cycles) prior to including it in a linear regression model. The optimal power is denoted by lambda, so $outcome^lambda$ becomes the transformed outcome variable.

```{r}
library(car)

(ans <-powerTransform(cbind(charges,age2) ~ 1, data=ins))
summary(ans)
```

The boxCox method can  be used to find a transformation of a response given a set of regressors.

```{r}
linear_model=lm(charges~sex+bmi+child_cat+smoker_num*bmi30+region+age2, data= data.frame(ins))
summary(linear_model)
boxCox(linear_model)
```

```{r}
ins$T_charges=ins$charges^-0.12
ins$T_age2=ins$age2^.33

```



```{r}
ins_training=ins[sample(1:1338,0.90*nrow(ins)),]
ins_testing=ins[sample(1:1338,0.10*nrow(ins)),]
```



In the begining, It is always helpful to have some idea of what the target feature is.


```{r,fig.height=8,fig.width=8}
hist(ins_testing$T_charges, breaks = 30)
```
```{r}
linear_model1=lm(T_charges~sex+bmi+child_cat+smoker_num*bmi30+region+T_age2, data=ins_training)
```





###  weighted (linear_model1)

```{r}

wts <- 1/fitted(lm(abs(ins_training$T_charges-ins_training$pred_ins) ~ predict(linear_model1, ins_training)))^2

```





```{r}
#install.packages("elasticnet", dependencies=TRUE, repos="http://cran.fhcrc.org")
WLS_linear_model1 <- lm(
T_charges~sex+bmi+child_cat+smoker_num*bmi30+region+T_age2,data=ins_training, weights=wts,
)
```




```{r}
#RMSE
ins_testing$pred_ins=predict(WLS_linear_model1,ins_testing)
ins_training$pred_ins=predict(WLS_linear_model1,ins_training)
print("RMSE-Training :")
print(RMSE(ins_training$T_charges, ins_training$pred_ins))
print("RMSE-Testing :")
print(RMSE(ins_testing$T_charges, ins_testing$pred_ins))
```





```{r}
#MSE
print("MSE-Training :")
print(mean(ins_training$T_charges-ins_training$pred_ins)^2)
print("MSE-Testing :")
print(mean(ins_testing$T_charges-ins_testing$pred_ins)^2)
```



```{r}
#Residual standard error for training dataset
print("RSE-Training :")

sqrt(sum((predict(WLS_linear_model1, ins_training)-ins_training$T_charges)^2)/
    (nrow(ins_training)-2))

print("RSE-Testing :")

sqrt(sum((predict(WLS_linear_model1, ins_testing)-ins_testing$T_charges)^2)/
    (nrow(ins_testing)-2))

```



```{r}

y=abs(((predict(WLS_linear_model1, ins_testing)-ins_testing$T_charges)^2)/
   (nrow(ins_testing)-2))
x=predict(WLS_linear_model1, ins_testing)
plot(x, y)
abline(lm(y~x), col="purple", lty=2)
loessLine(x,y,col="blue",log.x = FALSE, log.y = FALSE, smoother.args=list())

```



```{r}
d<-density((((predict(WLS_linear_model1, ins_testing)-ins_testing$T_charges))))
  
plot(d,main='Residual KDE Plot',xlab='Residual value')
```



```{r}
d=(((predict(WLS_linear_model1, ins_testing)-ins_testing$T_charges)))
plot(ecdf(d))
```


```{r}
shapiro.test(d)
```




```{r}
# diagnostic plots
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page
plot(WLS_linear_model1)
```





































